A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex

To understand the behavior of eval we perform a combination of static
analysis, dynamic analysis and manual inspection. The results presented
here summarize our findings.

@@

Some languages have chosen to restrict \eval. The essential difference
between languages relates to scoping of variables that can be accessed from
code executed by \eval.  Java and Julia are among the more restrictive
languages. In Java, \eval must be synthesized as a combination dynamic
loading and reflection.\footnote{While Java does not have \eval built in,
  one can take the input to \eval, wrap it in a static method of an
  anonymous class, generate bytecode for that class, invoke the Java class
  loader to dynamically install it, and then use reflection to call the new
  method.} Julia provides \eval more directly but limits its scope to top
level variables and methods. JavaScript support both a, so-called, global
\eval, and a local \eval. Where the latter has acces to local variables of
the function being executed (as well as variables of lexically enclosing
scopes). Finally languages such as R allow \eval to manipulate variables
defined in the caller environment of the function in which \eval is invoked.

>>>>

To understand the behavior of eval we perform a combination of static
analysis, dynamic analysis and manual code inspection. The results presented
here summarize our findings.

@@

Some languages have chosen to restrict \eval. The essential difference
between languages relates to scoping of variables that can be accessed from
code executed by \eval.  Java and Julia are among the more restrictive
languages. In Java, \eval must be synthesized as a combination dynamic
loading and reflection.\footnote{While Java does not have \eval built-in,
  one can take the input to \eval, wrap it in a static method of an
  anonymous class, generate bytecode for that class, invoke the Java class
  loader to dynamically install the new code, and then use reflection to
  call the new method.} Julia provides \eval more directly but limits its
scope to top level variables and methods. JavaScript support both a,
so-called, global \eval, and a local \eval. Where the latter has acces to
local variables of the function being executed (as well as variables of
lexically enclosing scopes). Finally languages such as R allow \eval to
manipulate variables defined in the caller environment of the function in
which \eval is invoked.
